Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-21 demystify.tex
Updates from Overleaf
updates

>>>>

\subsection{Common Pitfalls to Avoid}\label{sec:sop-pitfalls}

SOP is crucial for making a strong impression on adcom reviewers. This outlines common pitfalls to avoid in your SOP.

\begin{enumerate}
    \item \textbf{Generic Statements}: Using vague or general statements that could apply to any applicant. For example, saying blank statements such as “I am passionate about computer science” without providing specific examples or evidence.
    \item \textbf{Not Customized for the University you're applying to}: Failing to mention why this univ is a good fit for you and which faculty members you want to work with.
    \item \textbf{Too Long}: Keep it nore more than 2 pages.  Adcom members have to read many applications and a long SOP can be a turn-off.

    \item \textbf{Lack of Passion or Motivation}: Failing to convey genuine enthusiasm for research and the specific program.
    \item \textbf{Grammatical and Typographical Errors}: Submitting an SOP filled with grammatical mistakes, typos, and poorly constructed sentences.
    \item \textbf{Excessive Self-Praise}: Overly boasting about achievements without providing concrete evidence or examples to back them up.
    \item \textbf{Irrelevant Information}: Including personal anecdotes or experiences that do not relate to the field of study or research interests.
    \item \textbf{Unrealistic Goals}: Stating research goals that are not feasible or that show a lack of understanding of the field’s current state.
    \item \textbf{Negative Tone}: Criticizing previous institutions, professors, or colleagues.
    \item \textbf{Failure to Address Fit}: Not explaining why you are a good fit for the program and how the program is a good fit for your goals.
    \item \textbf{Generic Opening and Closing Statements}: Starting or ending the SOP with clichés or unoriginal statements that do not add value.
    \item \textbf{Lack of Customization}: Submitting the same SOP to multiple programs without tailoring it to each specific program's strengths and faculty.
\end{enumerate}
